Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-21 pkg/disttree/inst/draft/rejoinder.Rnw
adaption to new results of Rain_distribution and further revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2346 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 7ebcc9e62debed3abf93f2f926af1ebb44bc0415

\item \emph{Supplement 2: Stationwise evaluation.}\\
The show that the more extensive cross-validation results -- obtained only
for one station (Axams) in the main manuscript -- are fairly typical,
they are extended to 14 other observation stations. This also incorporates
results that were previously presented in Appendix B which has consequently
been omitted from the main manuscript.

@@

However, in our applications pre-pruning is disabled which
is explained in \dots \fixme{Improve Appendix~A to better
reflect this. Also align with the other comments about
alpha.}

@@

Therefore, we followed your advice and considered both a different
distribution for the continuous part and a two-part hurdle model.
For the former, the logistic distribution (also left-censored at zero)
is used as it has heavier tails and was previously used in the
precipitation forecasting literature \fixme{add reference}.
For the latter, a two-part model is used combining a binary
zero hurdle ($y = 0$ vs.\ $y > 0$) and an adjusted Gaussian distribution
(left-truncated at zero).

We have carried out the
same evaluations as presented in the main manuscript and present
the full results in Supplement 1 (Different Response Distributions). 
The main insights from this are also discussed in Section~4:
At most stations the censored Gaussian manuscript from the main
manuscript performs at least as well as the two alternative
distributions, if not better. Moreover, the distributional forest
proves to be rather robust against distributional misspecifications.
Therefore, the discussion in the main manuscript is still based
on the censored Gaussian distribution.

@@

Our manuscript follows the frequently-used approach of applying a
power-transformation (Stidd 1973, Hutchinson 1998, Stauffer et al.\ 2017)
to be more easily comparable to previous publications in the field.
These focus on predicting location and scale based on mean and
variance from the NWP ensemble. Hence, we also follow that approach
but adopt a different strategy for estimating selecting variables
and estimating nonlinear effects and interactions.

@@

\item[] Stauffer, R., Mayr, G. J., Messner, J. W., Umlauf, N. and Zeileis, A. (2017). 
Spatio-Temporal Precipitation Climatology over Complex Terrain Using a Censored Additive Regression Model,
\textit{International Journal of Climatology} \textbf{37, 7}: 3264--3275.

>>>>

\item \emph{Supplement 2: Stationwise evaluation.}\\
To show that the more extensive cross-validation results -- obtained only
for one station (Axams) in the main manuscript -- are fairly typical,
they are extended to 14 other observation stations. This also incorporates
results that were previously presented in Appendix B which has consequently
been omitted from the main manuscript.

@@

However, in our applications pre-pruning is disabled which
is explained in Section~3.2 and in the appendix.

@@

Therefore, we followed your advice and considered both a different
distribution for the continuous part and a two-part hurdle model.
For the former, the logistic distribution (also left-censored at zero)
is used as it has heavier tails and was previously used in the
precipitation forecasting literature (Stauffer et al.\ 2017b).
For the latter, a two-part model is used combining a binary
zero hurdle ($y = 0$ vs.\ $y > 0$) and an adjusted Gaussian distribution
(left-truncated at zero).

We have carried out the same evaluations as presented in the main manuscript and 
present the full results in Supplement 1 (Different Response Distributions). 
The main insights from this are also discussed in Section~4:
At most stations the censored Gaussian distribution from the main
manuscript performs at least as well as the two alternative
distributions. %, if not better. 
Moreover, the distributional forest proves to be rather robust against distributional
misspecifications. Therefore, the discussion in the main manuscript is still based
on the censored Gaussian distribution.

@@

Our manuscript follows the frequently-used approach of applying a
power-transformation (Stidd 1973, Hutchinson 1998, Stauffer et al.\ 2017a)
to be more easily comparable to previous publications in the field.
These focus on predicting location and scale based on mean and
variance from the NWP ensemble. Hence, we also follow that approach
but adopt a different strategy for estimating selecting variables
and estimating nonlinear effects and interactions.

@@

\item[] Stauffer, R., Mayr, G. J., Messner, J. W., Umlauf, N. and Zeileis, A. (2017a). 
Spatio-Temporal Precipitation Climatology over Complex Terrain Using a Censored Additive Regression Model,
\textit{International Journal of Climatology} \textbf{37, 7}: 3264--3275.

\item[] Stauffer, R., Umlauf, N., Messner, J. W., Mayr, G. J. and Zeileis, A. (2017b). 
Ensemble Post-Processing of Daily Precipitation Sums over Complex Terrain Using Censored High-Resolution Standardized Anomalies,
\textit{Monthly Weather Review} \textbf{45, 3}: 955--969.
%doi = 10.1175/mwr-d-16-0260.1
